---
title: "Sentiment Analysis with TidyText"
output: html_notebook
---

Congratulations on completing the Data Science Tech Talent South course! 
In this project you will be using R and TidyText for sentiment analysis on old essays that you've completed in undergrad. You will need to install TidyText for the sentiment analysis and qdaptools to load the .docx files. 
Here is a text on using TidyText to guide you (https://www.tidytextmining.com/sentiment.html)

```{r}
library(tidyverse)
library(tidytext)
library(qdapTools)
library(purrr)
library(data.table)
library(dplyr)
library(stringr)
get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")
```

First, load an essay into R using the read_docx function of the qdaptools library.

```{r}
#Suggestion for loading
#multiple
#essays <- lapply(Sys.glob("data/*.docx"), read_docx)
#single
#essay <- read_docx("data/myEssay1.docx")


```

Next remove the bibliography / reference section and the title page (grepl can help find the bibliography and checking the length of the character array can help determine if something is not a paragraph)

```{r}
#Suggestion for removing bibliography
#for (i in 1:length(essays)){
#  markForTruncation <- 0
#  for (j in 1:length(essays[[i]])){
#    if(grepl("^[Bb]ibliography|[[Rr]eferences|BIBLIOGRAPHY|REFERENCES", essays[[i]][[j]], fixed = FALSE)){
#      markForTruncation <- j
#    }
#  }
#  if(markForTruncation != 0){
#    essays[[i]] <- essays[[i]][1:markForTruncation-1]
#  }
#}


```

Next we have to split the essay into words with a line(sentence) and paragraph number in this format:
tbl_df:
column<fctr> column<int>   column<int>  column<chr>
essay        linenumber    paragraph    word
Or you could find a way to use TidyText with data in a different format

```{r}


```

Now we can simply can start applying the same logic used by the TidyText documentation (see examples in the link in the initial prompt)
Complete the following:
1. Bind rows to join sections of text to find the overall sentiment for paragraphs
2. Use ggplot to plot the sentiment of each chapter
3. Try creating a loop that will follow this process for multiple essays and compare the change in sentiments

This is your project, take it whatever direction you like!


```{r}
#1

```

```{r}
#2

```

